%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Job title
    {Juniper Networks} % Organization
    {Poznań, Poland} % Location
    {Jan. 2018 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of Contrail SDN department}
        \item {Developing Contrail Cloud - Red Hat OpenStack based platform integrated with Contrail SDN }
        \item {Improving integration of Contrail SDN with K8s, OpenShift and public clouds}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Principal Deployment Engineer} % Job title
    {Mirantis} % Organization
    {Poznań, Poland} % Location
    {Aug. 2014 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with clients to solve real life use cases using Cloudify orchestrator to provision different
               kinds of VNFs like vMX, Vyatta, docker containers on OpenStack and Kubernetes clusters.
               Developed python cloudify's plugins, TOSCA blueprints, docker images. Utilized SFC in OpenContrail SDN.}
        \item {One of the main contributors in FUEL@OPNFV project, successfully delivered 3 main releases.
               Learned how to efficiently work in open source project. Cooperated with different working groups
               focused on preparing CI/CD jobs for validation of NFV solution like OpenDaylight SFC, dpdk, kernel-rt.
               Involved in debug sessions. As a core reviewer both developed and reviewed puppet, python, bash code.}
        \item {Created \underline{\href{https://github.com/openstack/fuel-plugin-opendaylight}{plugin}}
               for Mirantis Fuel which integrate OpenDaylight SDN controller. Gained more experience with network part
               of OpenStack, OpenDaylight SDN controller and Open vSwitch.}
        \item {Created \underline{\href{https://github.com/NetApp/puppet-eseries/graphs/contributors}{puppet module}}
               for NetApp E-Series storage arrays. Learned how to manage remote network devices with puppet
               and write tests for own modules. Developed custom providers in ruby to use available REST API.}
        \item {Worked with US and EU customers, on site and remote, deploying and maintaining OpenStack and related technologies.}
        \item {Member of R\&D group which evaluated new NFV products, prepared proof of concepts, designed new solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {Oktawave} % Organization
    {Warsaw, Poland} % Location
    {Oct. 2012 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gained experience with managing VMware based public cloud.}
        \item {Being On-Call, improving monitoring system and automate recovery procedures.}
        \item {Maintained public object storage based on OpenStack Swift technology.}
        \item {Created a ruby program for optimal distribution of VMs disk files across storage nodes, using VMware API and MSSQL.}
        \item {Automated system administration tasks and unified server's configuration with Puppet.}
        \item {Deployment and tuning of ELK stack.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Administrator} % Job title
    {AGH University of Science and Technology} % Organization
    {Cracow, Poland} % Location
    {Nov. 2011 - Oct. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented distributed IT infrastructure monitoring system using Nagios core, check\_mk, pnp4nagios.}
        \item {Installed and configured high availability cluster virtualization platform based on VMware vSphere 5.}
        \item {Provided possibility to create and manage Git repositories with Gitolite, integrated with existing services: LDAP, Track.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Linux System Administrator} % Job title
    {radiofonia.fm} % Organization
    {Cracow, Poland} % Location
    {Jan. 2010 – Nov. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented backup system using the Bacula tool.}
        \item {Created development and production environment for KVM virtual machines and OpenVZ containers based on Proxmox platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
